\section*{Academic experience {\small Conferences}}

\begin{paracol}{2}
  2021
\switchcolumn
  \cvImportant{Member of the Programme Committee (ECON track)}\\
  GECCO2021, the \href{https://gecco-2021.sigevo.org/index.html/HomePage}{The Genetic and Evolutionary Computation Conference}.
  Lille, France.
\end{paracol}

\begin{paracol}{2}
  2020
\switchcolumn
  \cvImportant{Member of the Programme Committee}\\
  ODS2020, Optimisation and Decision Science 2020 with theme ``Optimisation in Artificial Intelligence and Data Science''.
  Rome, Italy.
\end{paracol}

\begin{paracol}{2}
  2020
\switchcolumn
  \cvImportant{Member of the Programme Committee (ECON track)}\\
  GECCO2020, the \href{https://gecco-2020.sigevo.org/index.html/HomePage}{The Genetic and Evolutionary Computation Conference}.
  Cancun, Mexico.
\end{paracol}

\begin{paracol}{2}
  2019
\switchcolumn
  \cvImportant{Member of the Programme Committee (ECON track)}\\
  GECCO2019, the \href{https://gecco-2019.sigevo.org/index.html/tiki-index.php}{The Genetic and Evolutionary Computation Conference}.
  Prague, Czech Republic.
\end{paracol}

\begin{paracol}{2}
  2019
\switchcolumn
  \cvImportant{Member of the Programme Committee}\\
  HM2019, the \href{https://web.archive.org/web/20180923151022/http://hm2019.ing.udec.cl/}{11\textsuperscript{th} International Workshop on Hybrid Metaheuristics}.
  Concepción, Chile.
\end{paracol}

\begin{paracol}{2}
  2018
\switchcolumn
  \cvImportant{Member of the Organising Committee} and \cvImportant{Session Chair}\\
  ODS 2018, \href{http://web.archive.org/web/20180923151224/http://www.airoconference.it/ods2018/committee}{Optimisation and Decision Science} Conference. Chair of the \href{https://santini.in/files/cv/ods18-prog.pdf}{``AIROYoung'' session}.
  Taormina, Italy.
\end{paracol}

\begin{paracol}{2}
  2018
\switchcolumn
  \cvImportant{Session Chair}\\
  \href{https://santini.in/files/cv/euro18-prog.pdf}{``EURO Young'' session} at the \href{http://web.archive.org/web/20180923151458/http://euro2018valencia.com/}{EURO 2018} Conference.
  Valencia, Spain.
\end{paracol}

\begin{paracol}{2}
  2018
\switchcolumn
  \cvImportant{Session Chair}\\
  \href{https://santini.in/files/cv/euroalio18-prog.pdf}{``AIROYoung'' session} at the \href{http://web.archive.org/web/20180923151741/https://events.unibo.it/euroalio2018}{EURO/ALIO 2018} Conference.
  Bologna, Italy.
\end{paracol}

\begin{paracol}{2}
  2017
\switchcolumn
  \cvImportant{Session Chair}\\
  \href{https://santini.in/files/cv/ods17-prog.pdf}{``AIROYoung'' session} at the ODS 2017, \href{http://web.archive.org/web/20180219031743/http://www.airoconference.it/ods2017/}{Optimisation and Decision Science} Conference.
  Sorrento, Italy.
\end{paracol}

\begin{paracol}{2}
  2016
\switchcolumn
  \cvImportant{Poster Session Chair}\\
  \href{https://santini.in/files/cv/airo16-prog.pdf}{``Young OR Researchers Poster Session''} at the \href{http://web.archive.org/web/20161031094953/http://www.airo.org/conferences/airo2016/}{AIRO 2016} Conference.
  Trieste, Italy.
\end{paracol}

\begin{paracol}{2}
  2016
\switchcolumn
  \cvImportant{Session Chair}\\
  \href{https://santini.in/files/cv/euro16-prog.pdf}{``Methodological advancements in metaheuristics'' session} at the \href{http://web.archive.org/web/20180923153214/https://euro2016.euro-online.org/}{EURO 2016} Conference.
  Poznan, Poland.
\end{paracol}

\begin{paracol}{2}
  2015
\switchcolumn
  \cvImportant{Session Chair}\\
  ``Exact Methods for Routing Problems'' at the \href{http://web.archive.org/web/20150924164917/http://www.airo.org/conferences/airo2015/}{AIRO 2015} Conference.
  Pisa, Italy.
\end{paracol}