\section*{Academic experience {\small Organisation}}

\begin{paracol}{2}
  \textsc{Jan 2019}
\switchcolumn
  \cvImportant{Member of the Programme Committee}\\
  ``HM 2019'', the 11\textsuperscript{th} International Workshop on Hybrid Metaheuristics.
  Concepción, Chile.
\end{paracol}

\begin{paracol}{2}
  \textsc{2018}
\switchcolumn
  \cvImportant{Founder}\\
  Founded \href{https://euroyoung.github.io/}{EUROYoung}, a group of young O.R.\ scientists from EURO member countries, with the aim of organising training events for early-stage researchers.
\end{paracol}

\begin{paracol}{2}
  \textsc{2016--18}
\switchcolumn
  \cvImportant{Coordinator}\\
  Coordinator of \href{https://www.airoyoung.org/}{AIROYoung}, the youth chapter of the \href{http://www.airo.org}{Italian Operational Research Association}.
  During my tenure as coordinator, I organised three workshops and a Ph.D.\ school, securing funding from Italian and European institutions;
  I created a database of young talents in O.R.\ and of open positions, helping matching O.R.\ scientists with relevant opportunities;
  I helped enroll new young members into AIRO, from Italy and other European countries.
\end{paracol}

\begin{paracol}{2}
  \textsc{Sep 2018}
\switchcolumn
  \cvImportant{Member of the Organising Committee} and \cvImportant{Session Chair}\\
  ``ODS 2018'' Conference. Chair of the ``AIROYoung'' session.
  Taormina, Italy.
\end{paracol}

\begin{paracol}{2}
  \textsc{Jun 2018}
\switchcolumn
  \cvImportant{Session Chair}\\
  ``EURO Young'' session at the EURO 2018 Conference.
  Valencia, Spain.
\end{paracol}

\begin{paracol}{2}
  \textsc{Jun 2018}
\switchcolumn
  \cvImportant{Session Chair}\\
  ``AIROYoung'' session at the EURO/ALIO 2018 Conference.
  Bologna, Italy.
\end{paracol}

\begin{paracol}{2}
  \textsc{Mar 2018}
\switchcolumn
  \cvImportant{Member of the Organising Committee}\\
  The 2\textsuperscript{nd} AIROYoung Workshop, on the theme ``Logistics optimisation and applied operational research''.
  Invited speakers: \href{https://scholar.google.it/citations?user=GXRnRZgAAAAJ&hl}{Geir Hasle} and \href{https://scholar.google.it/citations?user=pNQZmwIAAAAJ}{Roberto Roberti}.
  Cosenza, Italy, \textsc{03--05 Mar 2018}.
\end{paracol}

\begin{paracol}{2}
  \textsc{Sep 2017}
\switchcolumn
  \cvImportant{Session Chair}\\
  ``AIROYoung'' session at the ODS 2017 Conference.
  Sorrento, Italy.
\end{paracol}

\begin{paracol}{2}
  \textsc{Feb 2017}
\switchcolumn
  \cvImportant{Workshop Organiser}\\
    Organised, together with Lavinia Amorosi, the 1\textsuperscript{st} AIROYoung Workshop, on the theme ``Emerging Optimization Problems on Complex Networks''.
    Invited speakers: \href{https://scholar.google.com/citations?user=koF66usAAAAJ}{Justo Puerto} and \href{https://scholar.google.com/citations?user=PcGjfV8AAAAJ}{Maria Grazia Scutellà}.
    Rome, Italy, \textsc{16--17 Feb 2017}.
\end{paracol}

\begin{paracol}{2}
  \textsc{2016}
\switchcolumn
  \cvImportant{Founder}\\
  Founder of \href{https://www.airoyoung.org}{AIROYoung}, the youth chapter of the \href{http://www.airo.org}{Italian Operational Research Association}.
\end{paracol}

\begin{paracol}{2}
  \textsc{Sep 2016}
\switchcolumn
  \cvImportant{Poster Session Chair}\\
  ``Young OR Researchers Poster Session'' at the AIRO 2016 Conference.
  Trieste, Italy.
\end{paracol}

\begin{paracol}{2}
  \textsc{Jul 2016}
\switchcolumn
  \cvImportant{Session Chair}\\
  ``Methodological advancements in metaheuristics'' at the EURO 2016 Conference.
  Poznan, Poland.
\end{paracol}

\begin{paracol}{2}
    \textsc{2016}
\switchcolumn
  \cvImportant{EURO Young Researchers OR Webinars Organiser}\\
  Organised a series of \href{http://santini.in/seminars}{OR webinars} by and for young researchers from all over the world, sponsored by \href{http://euro-online.org}{EURO}.
\end{paracol}

\begin{paracol}{2}
  \textsc{Sep 2015}
\switchcolumn
  \cvImportant{Session Chair}\\
  ``Exact Methods for Routing Problems'' at the AIRO 2015 Conference.
  Pisa, Italy.
\end{paracol}

\begin{paracol}{2}
  \textsc{2015}
\switchcolumn
  \cvImportant{Seminars Organiser}\\
  Organised of a series of doctoral seminars within the Operational Research group at DEI, University of Bologna, involving local and visiting researchers.
\end{paracol}

\section*{Academic experience {\small Teaching}}

\begin{paracol}{2}
  \textsc{2019}
\switchcolumn
  \cvImportant{Practical Data Science for Operations Management}\\
  Barcelona School of Management, Pompeu Fabra University, M.Sc.\ in Management.
\end{paracol}

\begin{paracol}{2}
  \textsc{2018}
\switchcolumn
  \cvImportant{Machine Learning}\\
  RWTH Business School, M.Sc.\ in Data Analytics and Decision Science.
\end{paracol}

\begin{paracol}{2}
  \textsc{2018}
\switchcolumn
  \cvImportant{Operations Management}\\
  Pompeu Fabra University, Bachelor's in Business Management Administration.
\end{paracol}

\begin{paracol}{2}
  \textsc{2018--19}
\switchcolumn
  \cvImportant{Operations Management}\\
  Pompeu Fabra University, Bachelor's in International Business Economics.
\end{paracol}

\begin{paracol}{2}
  \textsc{2017}
\switchcolumn
  \cvImportant{Optimisation methods for Big Data Analytics}\\
  RWTH Aachen, Master's in Management, Business, and Economics.\\
  Student evaluation: 1.5 (on a scale where 1.0 is the best evaluation, and 5.0 is the worst).
\end{paracol}

\begin{paracol}{2}
  \textsc{2016--17}
\switchcolumn
  \cvImportant{Foundations of OR (teaching assistant)}\\
  A-K cohort taught by \href{https://scholar.google.com/citations?user=3nD4vYkAAAAJ}{Enrico Malaguti}, L-Z cohort taught by \href{https://scholar.google.com/citations?user=wORMYBMAAAAJ}{Michele Monaci}.\\
  M.Eng.\ in Management Engineering, University of Bologna.
\end{paracol}

\begin{paracol}{2}
  \textsc{2014--18}
\switchcolumn
  \cvImportant{Optimisation Algorithms (teaching assistant)}\\
  Course taught by \href{https://scholar.google.com/citations?user=2IPL4XIAAAAJ}{Paolo Toth}.\\
  M.Eng.\ in Computer Engineering, University of Bologna.
\end{paracol}

\section*{Academic experience {\small Evaluation Commitees}}

\begin{paracol}{2}
  \textsc{2018}
\switchcolumn
  \cvImportant{Grant proposal evaluator}\\
  ``FONDECYT Initiation into Research'' programme, Chilean National Science and Technology Commission.
\end{paracol}

\begin{paracol}{2}
  \textsc{2018}
\switchcolumn
  \cvImportant{Member of the MSc Thesis Defence Committee}\\
  Master in Statistics and Operational Research, Polytechnic University of Catalunya.
\end{paracol}

\section*{Academic experience {\small Visiting Positions}}

\begin{paracol}{2}
  \textsc{Nov 2017}
\switchcolumn
  \cvImportant{INSEC-TEC, Portugal}\\
  Visiting as part of a Short-Term Scientific Mission for COST Action ``European Network for Collaboration on Kidney Exchange Programmes''.
  Working with \href{https://scholar.google.com/citations?user=RW7QevYAAAAJ}{Ana Viana}, \href{https://scholar.google.it/citations?user=aWTZf_AAAAAJ}{João Pedro Pedroso}, and \href{http://orcid.org/0000-0003-1085-0810}{Xenia Klimentova}.
\end{paracol}

\begin{paracol}{2}
  \textsc{Jul-Oct 2016}
\switchcolumn
  \cvImportant{Amazon Inc.}\\
  Visiting Research Scientist in Seattle, USA. Working with \href{https://scholar.google.com/citations?user=KTmPx50AAAAJ}{Mauricio Resende} and \href{https://scholar.google.it/citations?user=U5iFVowAAAAJ}{Andrew Goldberg}.
\end{paracol}

\begin{paracol}{2}
  \textsc{Feb 2016}
\switchcolumn
  \cvImportant{Vrije Universiteit Amsterdam}\\
  Visiting PhD Student at the Department of Information, Logistics and Innovation. Working with \href{https://scholar.google.com/citations?user=wjjCd5UAAAAJ}{Wout Dullaert}.
\end{paracol}

\begin{paracol}{2}
  \textsc{Nov 2015}
\switchcolumn
  \cvImportant{University of Calabria}\\
  Visiting PhD Student at the Department of Mechanical, Energy and Management Engineering. Working with \href{https://scholar.google.com/citations?user=r_qFOqgAAAAJ}{Demetrio Laganà}.
\end{paracol}

\begin{paracol}{2}
  \textsc{Mar-May 2015}
\switchcolumn
  \cvImportant{Danish Technical University (DTU)}\\
  Visiting PhD Student at the Department of Management Engineering. Working with \href{https://scholar.google.com/citations?user=sYi141QAAAAJ}{Stefan Røpke}.
\end{paracol}

% \section*{Academic experience {\small Research Groups Membership}}
%
% \begin{paracol}{2}
%   \textsc{2014--15}
% \end{paracol}
% \begin{minipage}[t]{0.85\textwidth}
%   \cvImportant{GNAMPA}, Gruppo Nazionale per l'Analisi Matematica, la Probabilità e le loro Applicazioni, INDAM.
% \end{paracol}

% \section*{Academic experience {\small Reviewer Duties}}
%
% \begin{paracol}{2}
%   \textsc{2014--17}
% \end{paracol}
% \begin{minipage}[t]{0.85\textwidth}
%   Reviewer for many international journals, including: Engineering Optimization, International Transactions in Operational Research, INFORMS Journal of Computing, Discrete and Applied Mathematics, 4OR.
% \end{paracol}
