\section*{Grants {\small Competitive}}

\begin{paracol}{2}
  \textsc{2018--20}
\switchcolumn
  \cvImportant{Juan de la Cierva Formación}\\
  Two-year grant from the Spanish government.
  \href{https://santini.in/files/cv/jdc17.pdf}{Ranked 1\textsuperscript{st} out of 49 participants from all areas of Mathematics, with a score of 99/100}.
\end{paracol}

\begin{paracol}{2}
  \textsc{2014--16}
\switchcolumn
  \cvImportant{Ph.D.\ grant by the \href{https://www.unibo.it}{University of Bologna}}\\
  \href{https://santini.in/files/cv/phd14.pdf}{Ranked 1\textsuperscript{st} out of 9 qualified participants, with a score of 92/100}.
  Funded: 40~915 Eur (three years).
\end{paracol}

\section*{Grants {\small Other}}

\begin{paracol}{2}
  \textsc{2019}
\switchcolumn
  \cvImportant{Yerun Mobility Award}\\
  To visit University \href{https://www.dauphine.psl.eu/}{Paris Dauphine}, sponsored by \href{https://www.yerun.eu}{YERUN}.
  Founded: 1~000 Eur.
\end{paracol}

\begin{paracol}{2}
  \textsc{Dec 2018}
\switchcolumn
  \cvImportant{Erasmus+ Grant}\\
  To visit the \href{https://www.unibo.it/}{University of Bologna}, through the \href{https://smarttranslog.wordpress.com/}{SmartTransLog} consortium.
  Founded: 1~200 Eur.
\end{paracol}

\begin{paracol}{2}
  \textsc{2017}
\switchcolumn
  \cvImportant{COST STSM Grant}\\
  Short-Term Scientific Mission grant to conduct research at \href{https://www.inesctec.pt/}{INESC-TEC} under \href{http://www.cost.eu/}{COST} Action \href{http://www.enckep-cost.eu/}{``European Network for Collaboration on Kidney Exchange Programmes''}.
  Funded: 1~500 Eur.
\end{paracol}

\begin{paracol}{2}
  \textsc{2016}
\switchcolumn
  \cvImportant{PRIN (Research Projects of Relevant National Interest) 2016}\\
  Part of the group awarded for the project \href{https://santini.in/files/cv/prin16.pdf}{``Transportation and Logistics Optimization in the Era of Big and Open Data''}.
  Total funded: 840~638 Eur.
\end{paracol}

\begin{paracol}{2}
  \textsc{2016}
\switchcolumn
  \cvImportant{\href{https://euro-online.org}{Association of European Operational Research Societies (EURO)}}\\
  Grant to organise the \href{https://www.airoyoung.org/resources/euro-seminars}{``EURO Young Researchers OR Webinars''}.
  Funded: 1~000 Eur.
\end{paracol}

\begin{paracol}{2}
  \textsc{2015}
\switchcolumn
  \cvImportant{Marco Polo scholarship}\\
  Grant to conduct research abroad.
  Funded: 1~878 Eur (three months).
\end{paracol}