\section*{Schools attended}

\begin{paracol}{2}
  \textsc{Oct 2015}
\switchcolumn
  Combinatorial Optimization at Work\\
  Zuse Institut (Germany)
  {\scriptsize\\
    Lectures by Martin Grötschel, Thorsten Koch, Robert Bixby, Pierre Bonami, etc.
  }
\end{paracol}

\begin{paracol}{2}
  \textsc{Jan 2015}
\switchcolumn
  The Aussois Combinatorial Optimization Workshop\\
  Aussois (France)
  {\scriptsize\\
    Invited by Silvano Martello.
  }
\end{paracol}

\begin{paracol}{2}
  \textsc{May 2014}
\switchcolumn
  VeRoLog school on VRP\\
  University of Bologna (Italy)
  {\scriptsize\\
    Lectures by Olli Bräysy, Roberto Baldacci, and Daniele Vigo.
  }
\end{paracol}

\begin{paracol}{2}
  \textsc{Feb 2014}
\switchcolumn
  Paris Spring School in Column Generation\\
  Institut Henri Poincaré (France)
  {\scriptsize\\
    Lectures by Marco Lübbecke, Guy Desaulniers, Jacques Desrosiers, and Roberto Wolfler-Calvo.
    % ``Column generation basics'' by Marco Lübbecke.\\
    % ``Constrained VRP and Shortest Path problems'' by Guy Desaulniers.\\
    % ``Dual point of view'' by Jacques Desrosiers.\\
    % ``Additive bounding'' by Roberto Wolfler-Calvo.
  }
\end{paracol}

\begin{paracol}{2}
  \textsc{Jun-Aug 2012}
\switchcolumn
  International Summer Programme\\
  Copenhagen Business School (Denmark)
  {\scriptsize\\
    Lectures by Rolando Tomasini and Gary Schwartz.
    % ``Introduction to purchasing in a globalized Market'' by Rolando Tomasini.\\
    % ``Leading and managing organizations'' by Gary Schwartz.
  }
\end{paracol}

\begin{paracol}{2}
  \textsc{Jul-Sep 2011}
\switchcolumn
  Inter-university Summer School in Mathematics\\
  Perugia University (Italy)
  {\scriptsize\\
    Lectures by Vitali Milman, Yuli Eidelman, and Sandy Zabell.
    % ``Functional analysis'' by Vitali Milman and Yuli Eidelman.\\
    % ``Probability'' by Sandy Zabell.
  }
\end{paracol}

\begin{paracol}{2}
  \textsc{Jun 2011}
\switchcolumn
  NIP Summer School\\
  Aberdeen University (Scotland)
  {\scriptsize\\
    Lectures by Crispin Wright, Brian Wetherson, and Alan Weir.
    % ``Relativism and objectivity'' by Crispin Wright.\\
    % ``Fallibilism and infallibilism'' by Brian Weatherson.\\
    % ``Truth and Paradox'' by Alan Weir.
  }
\end{paracol}

\begin{paracol}{2}
  \textsc{Aug-Sep 2010}
\switchcolumn
  Rome-Moscow school of Matrix Methods and Applied Linear Algebra\\
  Rome 2 University (Italy), Moscow State University (Russia)
  {\scriptsize\\
    Lectures by Evgeny Tyrtyshnikov, Carmine Di Fiore, Paolo Zellini, Daniele Bertaccini, Hakim Ikramov, Raymond Chan, and Sergey Grudsky.
    % ``Future of tensor computations'' by Evgeny Tyrtyshnikov.\\
    % ``Matrix structures and applications'' by Carmine Di Fiore, Paolo Zellini, Daniele Bertaccini.\\
    % ``Condensed forms for matrices under unitary similarities and congruences'' by Hakim Ikramov.\\
    % ``A unified tight-frame approach for missing data recovery in images'' by Raymond Chan.\\
    % ``Eigenvalues of large Toeplitz matrices: asymptotic approach'' by Sergey Grudsky.
  }
\end{paracol}