\section*{Supervised projects and theses}

\begin{paracol}{2}
  \textsc{Apr-Sep 2017}
\switchcolumn
  \cvImportant{Project, M.Sc.\ in Management, Business, and Economics, RWTH Aachen}\\
  Supervisor, ``Improving document-level machine translation with \texttt{\scriptsize word2vec}'', Sean Eulenberg.
\end{paracol}

\begin{paracol}{2}
  \textsc{Apr-Sep 2017}
\switchcolumn
  \cvImportant{Master's Thesis, M.Sc. in Management, Business, and Economics, RWTH Aachen}\\
  Co-supervisor, ``A heuristic algorithm for the electric pickup and delivery problem'', Lutz Venhofen.
\end{paracol}

\begin{paracol}{2}
  \textsc{Sep-Dec 2016}
\switchcolumn
  \cvImportant{Master's Thesis, M.Eng. in Management Engineering, University of Bologna}\\
  Co-supervisor, ``Embedding robustness in train rescheduling algorithms'', Alessandro Morandi.
\end{paracol}

\begin{paracol}{2}
  \textsc{Feb-Apr 2016}
\switchcolumn
  \cvImportant{Project, M.Eng. in Computer Engineering, University of Bologna}\\
  Co-supervisor, ``A genetic algorithm for real-time energy optimisation of train timetables'', Francesco Di Lella.
\end{paracol}

\begin{paracol}{2}
  \textsc{Sep-Dec 2015}
\switchcolumn
  \cvImportant{Master's Thesis, M. Eng. in Management Engineering, University of Bologna}\\
  Co-supervisor, ``Metaheuristic algorithms for energy optimisation in train timetabling and rescheduling'', Hang Xu.
\end{paracol}

\begin{paracol}{2}
  \textsc{Mar-Jun 2015}
\switchcolumn
  \cvImportant{Project, M.Eng. in Computer Engineering, University of Bologna}\\
  Co-supervisor, ``A constructive heuristic for the dispatching problem on multi-track territories'', Giacomo Dall'Olio and Simone Laierno.
\end{paracol}

\begin{paracol}{2}
  \textsc{Aug-Nov 2014}
\switchcolumn
  \cvImportant{Master's Thesis, M.Eng. in Management Engineering, University of Bologna}\\
  Co-supervisor, ``Valutazione della Performance di un caso di Customer Contact Desk attraverso l'applicazione della metodologia Data Envelopment Analysis'', Martina Carli.
\end{paracol}
