\section*{Supervised theses}

\begin{paracol}{2}
  2020
\switchcolumn
  \cvImportant{Project, \href{https://www.business-school.rwth-aachen.de/en/programs/m-sc-data-analytics-and-decision-science/}{M.Sc.\ in Data Analytics and Decision Science}, \href{https://www.business-school.rwth-aachen.de/en/}{RWTH Business School}}\\
  Supervisor, ``COVID-19 Pandemic: Comparison of forecasting methodologies and affecting factors for fatalities and transmission rates'', Peter Yacoub.

  \cvImportant{Project, \href{https://www.business-school.rwth-aachen.de/en/programs/m-sc-data-analytics-and-decision-science/}{M.Sc.\ in Data Analytics and Decision Science}, \href{https://www.business-school.rwth-aachen.de/en/}{RWTH Business School}}\\
  Supervisor, ``Machine learning for selective assembly with automatic adaption to use-case complexity'', Sourabh Hujare.

  \cvImportant{Bachelor's Thesis, \href{https://www.upf.edu/web/econ/}{School of Economics and Business}, \href{https://www.upf.edu/}{Universitat Pompeu Fabra}}\\
  Supervisor, ``Congestion tax as the optimal policy tool to minimize congestion in the city of Barcelona'', Joel Sanginés-Uriarte Dooly and Adrià Trepat i Izquierdo.

  \cvImportant{Bachelor's Thesis, \href{https://www.upf.edu/web/econ/}{School of Economics and Business}, \href{https://www.upf.edu/}{Universitat Pompeu Fabra}}\\
  Supervisor, ``Machine Learning for Price Discrimination'', Jan Czernek.
\end{paracol}

\begin{paracol}{2}
  2019
\switchcolumn
  \cvImportant{Erasmus+ Internship, incoming from the \href{https://www.utwente.nl/}{University of Twente}}\\
  Supervisor, ``Production planning and optimisation of vertical farms'', Vinicius Greco de Lemos.

  \cvImportant{Master's Thesis, \href{https://www.bsm.upf.edu/en/master-of-science-in-management-specialization-in-business-analytics}{M.Sc.\ in Management}, \href{https://www.bsm.upf.edu/}{Barcelona School of Management}, \href{https://www.upf.edu/}{Universitat Pompeu Fabra}}\\
  Supervisor, ``Demand forecasting model in food delivery, a heuristic approach to data science using Python and geoanalysis'', Marc Herrera.
\end{paracol}

\begin{paracol}{2}
  2017
\switchcolumn
  \cvImportant{Project, \href{http://www.wiwi.rwth-aachen.de/cms/Wirtschaftswissenschaften/Studium/Studiengaenge/Masterstudiengaenge/~camq/Wirtschaftswissenschaft-M-Sc-/?lidx=1}{M.Sc.\ in Management, Business, and Economics}, \href{https://www.rwth-aachen.de/}{RWTH Aachen}}\\
  Supervisor, ``Improving document-level machine translation with \texttt{\scriptsize word2vec}'', Sean Eulenberg.

  \cvImportant{Master's Thesis, \href{http://www.wiwi.rwth-aachen.de/cms/Wirtschaftswissenschaften/Studium/Studiengaenge/Masterstudiengaenge/~camq/Wirtschaftswissenschaft-M-Sc-/?lidx=1}{M.Sc.\ in Management, Business, and Economics}, \href{https://www.rwth-aachen.de/}{RWTH Aachen}}\\
  Co-supervisor, ``A heuristic algorithm for the electric pickup and delivery problem'', Lutz Venhofen.
\end{paracol}

\begin{paracol}{2}
  2016
\switchcolumn
  \cvImportant{Master's Thesis, \href{https://corsi.unibo.it/magistrale/IngegneriaGestionale}{M.Eng.\ in Management Engineering}, \href{https://www.unibo.it}{University of Bologna}}\\
  Co-supervisor, ``Embedding robustness in train rescheduling algorithms'', Alessandro Morandi.

  \cvImportant{Project, \href{https://corsi.unibo.it/magistrale/ingegneriainformatica}{M.Eng.\ in Computer Engineering}, \href{https://www.unibo.it}{University of Bologna}}\\
  Co-supervisor, ``A genetic algorithm for real-time energy optimisation of train timetables'', Francesco Di Lella.
\end{paracol}

\begin{paracol}{2}
  2015
\switchcolumn
  \cvImportant{Master's Thesis, \href{https://corsi.unibo.it/magistrale/IngegneriaGestionale}{M.Eng.\ in Management Engineering}, \href{https://www.unibo.it}{University of Bologna}}\\
  Co-supervisor, ``Metaheuristic algorithms for energy optimisation in train timetabling and rescheduling'', Hang Xu.

  \cvImportant{Project, \href{https://corsi.unibo.it/magistrale/ingegneriainformatica}{M.Eng.\ in Computer Engineering}, \href{https://www.unibo.it}{University of Bologna}}\\
  Co-supervisor, ``A constructive heuristic for the dispatching problem on multi-track territories'', Giacomo Dall'Olio and Simone Laierno.
\end{paracol}

\begin{paracol}{2}
  2014
\switchcolumn
  \cvImportant{Master's Thesis, \href{https://corsi.unibo.it/magistrale/IngegneriaGestionale}{M.Eng.\ in Management Engineering}, \href{https://www.unibo.it}{University of Bologna}}\\
  Co-supervisor, ``Valutazione della Performance di un caso di Customer Contact Desk attraverso l'applicazione della metodologia Data Envelopment Analysis'', Martina Carli.
\end{paracol}
